### 2020-03-24 thesis_template/3_Body/model/drop_ref_rc.tex
change

The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.

@@

The result shows the time to drop borrowing reference is significatly faster than reference counting. This says that we should use borrwoing storategies whenever high performance computation is critical.

\begin{figure}[htb!]
    \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
    \caption{Runtime for Droping to fields of Customer Object}
    \label{fig:Sampling}
\end{figure}

>>>>

\subsection{Concept}
The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.

@@

\subsection{Result}
The result shows the time to drop borrowing reference is significatly faster than reference counting. This says that we should use borrwoing storategies whenever high performance computation is critical.
\begin{figure}[htb!]
    \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
    \caption{Runtime for Droping to fields of Customer Object}
    \label{fig:Sampling}
\end{figure}

\subsection{Discussion}
